---
title: "Decision Tree Homework"
output: html_notebook
---
# MVP 

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(GGally)

library(tidyverse)
titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]

```
# Question 1

```{r}
View(titanic_set)

titanic_set_clean  <- 
  titanic_set %>% 
  drop_na %>% 
  mutate(sex = as.factor(sex), survived = as.factor(survived), pclass = as.factor(pclass),embarked = as.factor(embarked)) %>% 
  mutate(age_status = if_else(age <= 16,"child", "adult")) %>% 
  mutate(age_status = as.factor(age_status)) %>% 
  select(-...1, -passenger_id, -name, -ticket, -fare, -cabin)
  


```


# Question 2 

```{r}
# it looks like sex and class are most important 

ggpairs(titanic_set_clean)
```
# Question 3 


```{r}

# I did 30/70 test/train since I have a small dataset. 

n_data <- nrow(titanic_set_clean)

test_index <- sample(1:n_data, size = n_data*0.3)

titanics_test  <- slice(titanic_set_clean, test_index)

titanics_train <- slice(titanic_set_clean, -test_index)

titanics_test %>%
 janitor::tabyl(survived)

titanics_train %>%
 janitor::tabyl(survived)

```

# Question 4

```{r}

titanics_fit <- rpart(
  formula = survived ~ ., 
  data = titanics_train, 
  method = 'class'
)

rpart.plot(titanics_fit, 
           yesno = 2, 
           fallen.leaves = TRUE, 
           faclen = 6, 
           digits = 4)

```

# Question 5

The variables in the plot (sex, age and sib_sp) are the ones that are most informative for predicting survival. A the top we can see that the probability of survival is 65 %. And then, if they are not male, we can see that the chance of survival was 93 %. If they were male, however, their chace of survival was 43%. If they were male and older than 36, the survival chance was 29 %, and if they were male and younger than 36 it's 61%. If a man then was younger than 31.5, his survival chance was 51%, and if he was between 31 and 36 his survival chance was 77 %. If he was younger than 31.5 and had a partner or sibling, his survival chance was 41%, but it was 70 % if he had no partner or siblings. 

# Question 6 

```{r}

library(modelr)

titanics_test_pred <- titanics_test %>%
  add_predictions(titanics_fit, type = 'class')

library(yardstick)

conf_mat <- titanics_test_pred %>%
              conf_mat(truth = survived, estimate = pred)

conf_mat

accuracy <- titanics_test_pred %>%
 accuracy(truth = survived, estimate = pred)

accuracy

```
The confusion matrix shows that 9 passengers who were predicted to die and who died, 33 passengers who survived and were predicted to survive, 6 passengers who died but were predicted to have survived, and six passengers who were predicted to die but survived.The model was accurate in 77% of cases. 


