---
title: "Manual model development"
output: html_notebook
---

## MVP 

Question 1 

```{r}
library(tidyverse)
library(modelr)
library(GGally)
library(ggfortify)

house_data <- read_csv("kc_house_data.csv")

```
```{r}
# check for missing values 

house_data %>% 
   summarise(across(everything(), ~sum(is.na(.x))))

# remove unnecessary columns, change yr_renovated to logical(renovated or not), remove aliased variables, change relevant numeric columns to factors.  

house_data_clean <- 
house_data %>% 
  select(-date, -id, -sqft_living15, - sqft_lot15, - zipcode, - sqft_basement) %>% 
  mutate(yr_renovated = if_else(yr_renovated > 0, TRUE, FALSE)) %>% 
  mutate(view = as.factor(view)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  mutate(grade = case_when(grade <= 3 ~ "unacceptable quality", grade >=  11 ~ "high quality", .default = "average quality" )) %>% 
  mutate(grade = as.factor(grade)) %>% 
  mutate(waterfront = as.factor(waterfront))



```

 Question 2 

```{r}

alias(lm(price ~ ., data = house_data_clean))

```

Question 3 


```{r}
ggpairs(house_data_clean)

houses_tidy_numeric <- house_data_clean %>%
  select_if(is.numeric)

houses_tidy_nonnumeric <- house_data_clean %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- house_data_clean$price

ggpairs(houses_tidy_numeric)
ggpairs(houses_tidy_nonnumeric)


```

The numeric variables that are most strongly correlated with price are bathrooms (0.5), sqft living (0.7), and sqft above (0.6).  

Categorical variables that seem of interest are waterfront, view, condition and grade. 


Start with the most strongly correlated numeric variable, sqft living. Autoplot doesn't look great. The model explains 0.4929 of the variance in house price. 

```{r}
mod_1 <- lm(price ~ sqft_living, data = house_data_clean)

summary(mod_1)

autoplot(mod_1)


```
add sqft above to the model. It is significant and explains more variance. 

```{r}

mod_2 <- lm(price ~ sqft_living + sqft_above, data = house_data_clean)

summary(mod_2)

autoplot(mod_2)

```
compare the two models 

```{r}
anova(mod_1, mod_2)
```

My model including sqft above is better since the anova is significant. 

Add bathrooms to the model. 

```{r}
mod_3 <- lm(price ~ sqft_living + sqft_above + bathrooms, data = house_data_clean)

summary(mod_3)

anova(mod_2, mod_3)
```
Adding bathrooms to the model does not explain significantly more of the variance, according to the anvova. 

Add categorical predictors to model 2. 


```{r}
# add waterfront 

mod_4 <- lm(price ~ sqft_living + sqft_above + waterfront, data = house_data_clean)

summary(mod_4)

autoplot(mod_4)

```

Waterfront is significant and more variance is explained. 

add view to the model 

```{r}

mod_5 <- lm(price ~ sqft_living + sqft_above + waterfront + view, data = house_data_clean)

summary(mod_5)

anova(mod_4, mod_5)

```
Adding view explains more of the variance and the anova is significant. 

Try other models. Model 6 explains more of the variance than model 2, so I will keep model 6 instead. 

```{r}
mod_6 <- lm(price ~ sqft_living + waterfront, data = house_data_clean)

summary(mod_6)

summary(mod_2)

```

add view to the model 

```{r}
mod_7 <- lm(price ~ sqft_living + waterfront + view, data = house_data_clean)

summary(mod_7)

anova(mod_6, mod_7)
```


It is significant, but R square doesnt increase that much if I add view. 

Try other categorical predictors after model 6. 

condition was not significant. 

```{r}

mod_8 <- lm(price ~ sqft_living + waterfront + condition, data = house_data_clean)

summary(mod_8)

```

```{r}
mod_9 <- lm(price ~ sqft_living + waterfront + grade, data = house_data_clean)

summary(mod_9)
```
R square increases a little if I add grade, possibly add. 

check for all predictors 

```{r}
mod_all <- lm(price ~ ., data = house_data_clean)

summary(mod_all)
```


All of them explains 68 % of the variance. Mod 6 explains 53 % of the variance. But mod 10, with view instead of waterfront explains more of the variance. 

```{r}

mod_10 <- lm(price ~ sqft_living + view, data = house_data_clean)

summary(mod_10)
```
I'll try adding waterfront. 

```{r}
mod_11 <- lm(price ~ sqft_living + view + waterfront, data = house_data_clean)

summary(mod_11)

anova(mod_10, mod_11)
```
The anova is significant, but not mych more of hte variance is explained. So I'll stick to mod 10. 

```{r}

anova(mod_11, mod_10)

final_model <- lm(price ~ sqft_living + view, data = house_data_clean)
```

## Extensions

test possible interactions - not really any interactions here. 

```{r}
house_data_clean %>% 
  ggplot(aes(x = sqft_living, y = price, colour = interaction(waterfront, view)))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

house_data_clean %>% 
  ggplot(aes(x = sqft_living, y = price, colour = view))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)

house_data_clean %>% 
  ggplot(aes(x = sqft_living, y = price, colour = waterfront))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)


```
```{r}
library(relaimpo)
calc.relimp(final_model, type = "lmg", rela = TRUE)
```

sqft_living accounts for 80 % of the variance and view for 20 %. 





