---
title: "Homework - CIs"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

<hr>

# MVP

Now we'll go back to CI creation in the normal fashion. We'll take the `ames` data from the CIs lab earlier today and regard it now as a **sample**, we won't be drawing any smaller samples from within it. This is the usual situation in an analysis: you use all the data available to you!



**Task 1.**  
Load the data again, `clean_names()`, and re-familiarise yourself with it


```{r}
ames <- read_csv("ames.csv") %>% 
  clean_names()
View(ames)
```


**Task 2.**  
Investigate the distribution of `lot_area`. Is the distribution roughly normal? If not, what problems do you find?

```{r}

ames %>%  
  ggplot(aes(x = lot_area)) +
  geom_histogram(colour = "white", fill = "indianred")

```
The data looks a little bit skewed. 

**Task 3.**  
Compute and visualise a bootstrap sampling distribution for the `mean(lot_area)` of the sold houses.


```{r}

infer_resample_ames <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 5000, type = "bootstrap") %>%  
  calculate(stat = "mean") 
  
infer_resample_ames

```


```{r}
infer_resample_ames %>% 
  visualise(bins = 30)

```


**Task 4.**  
Use your bootstrap distribution to calculate a $95\%$ CI for `mean(lot_area)`, and visualise it on the distribution


```{r}

infer_ci_95_ames <- infer_resample_ames %>% 
  get_ci(level = 0.95, type = "percentile")


infer_resample_ames %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_95_ames)

```

**Task 5.**  
You would like to know the `mean(lot_area)` of the sold houses with higher confidence. Calculate the $99\%$ CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the $95\%$ CI? Does that make sense?

```{r}
infer_ci_99_ames <- infer_resample_ames %>% 
  get_ci(level = 0.99, type = "percentile")

infer_resample_ames %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_99_ames)


```
It does make sense, the confidence interval has gotten wider.  

**Task 6.**  
Calculate the point estimate of the `mean(lot_area)`

```{r}

mean_infer_ames <- infer_resample_ames %>% 
  summarise(mean = mean(stat))

mean_infer_ames 

```


# Extension

<br>

**Task 1.**  
Calculate a point estimate and $95\%$ CI for the proportion of houses in the data built before 1920.  Does the number of `reps` you use matter? [Investigate `reps` from $200$ up to $50000$, memory of your laptop permitting].
<br><br>


```{r}

# Make a new column of yes and no for either built before or after 1920. 

ames_new <- ames %>% 
  mutate(before_after = ifelse(year_built < 1920, "yes", "no"))
  

infer_resample_ames_prop <- ames_new %>% 
  specify(respons = before_after, success = "yes") %>% 
  generate(reps = 5000, type = "bootstrap") %>%  
  calculate(stat = "prop") 
  
infer_resample_ames_prop

years_ci_95 <- infer_resample_ames_prop %>% 
  get_ci(level = 0.95, type = "percentile")

years_ci_95

infer_resample_ames_prop %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = years_ci_95)

mean_years <- ames_new %>% 
  summarise(point_est = mean(before_after == "yes"))

mean_years


```
Appears to be 6%. 

```{r}
# try 200 reps 

infer_resample_ames_prop_200 <- ames_new %>% 
  specify(respons = before_after, success = "yes") %>% 
  generate(reps = 200, type = "bootstrap") %>%  
  calculate(stat = "prop")

# new CI 

years_ci_95_200 <- infer_resample_ames_prop_200 %>% 
  get_ci(level = 0.95, type = "percentile")

years_ci_95_200

# between 0.53 and 0.068

```
```{r}
# try 50000

infer_resample_ames_prop_50000 <- ames_new %>% 
  specify(respons = before_after, success = "yes") %>% 
  generate(reps = 50000, type = "bootstrap") %>%  
  calculate(stat = "prop")

# new CI 

years_ci_95_50000 <- infer_resample_ames_prop_50000 %>% 
  get_ci(level = 0.95, type = "percentile")

years_ci_95_50000

#  width generally decreases as sample size increases

# 0.051 - 0.068 
```
The confidence intervals seem to increase as sample size increase which is unexpected, or not change much at all.




